---
title: "Twitter"
author: "Chiayu"
date: "August 2019"
output:
  html_document:
    theme: spacelab
    toc: yes
    toc_float:
      collapsed: no
    df_print: paged
editor_options:
  chunk_output_type: inline
---
<style>

body {
    color: #333333;
    font-size: 14px;
}

</style>




## 01 prepare
### 1.1 packages

* `install.packages()` ,`library()`

```{r echo=TRUE, warning=FALSE}
options(knitr.table.format = "html")
options(stringsAsFactors = FALSE)
library(pacman)
p_load(tidyverse,tidytext,lubridate,dplyr,ggplot2,stringr,RColorBrewer,knitr,bbplot,prettydoc,kableExtra,jiebaRD,jiebaR)
```

### 1.2 plot in chinese

* `bbc_style_cn()` 
```{r include=FALSE}
bbc_style_cn <- function() {
  font <- "Gen Jyuu GothicX"
  ggplot2::theme(
    #Text format:
    #This sets the font, size, type and colour of text for the chart's title
    plot.title = ggplot2::element_text(family=font,
                                       size=28,
                                       face="bold",
                                       color="#222222"),
    #This sets the font, size, type and colour of text for the chart's subtitle, as well as setting a margin between the title and the subtitle
    plot.subtitle = ggplot2::element_text(family=font,
                                          size=22,
                                          margin=ggplot2::margin(9,0,9,0)),
    plot.caption = ggplot2::element_blank(),
    #This leaves the caption text element empty, because it is set elsewhere in the finalise plot function
    #Legend format
    #This sets the position and alignment of the legend, removes a title and backround for it and sets the requirements for any text within the legend. The legend may often need some more manual tweaking when it comes to its exact position based on the plot coordinates.
    legend.position = "top",
    legend.text.align = 0,
    legend.background = ggplot2::element_blank(),
    legend.title = ggplot2::element_blank(),
    legend.key = ggplot2::element_blank(),
    legend.text = ggplot2::element_text(family=font,
                                        size=18,
                                        color="#222222"),
    #Axis format
    #This sets the text font, size and colour for the axis test, as well as setting the margins and removes lines and ticks. In some cases, axis lines and axis ticks are things we would want to have in the chart - the cookbook shows examples of how to do so.
    axis.title = ggplot2::element_blank(),
    axis.text = ggplot2::element_text(family=font,
                                      size=18,
                                      color="#222222"),
    axis.text.x = ggplot2::element_text(margin=ggplot2::margin(5, b = 10)),
    axis.ticks = ggplot2::element_blank(),
    axis.line = ggplot2::element_blank(),
    #Grid lines
    #This removes all minor gridlines and adds major y gridlines. In many cases you will want to change this to remove y gridlines and add x gridlines. The cookbook shows you examples for doing so
    panel.grid.minor = ggplot2::element_blank(),
    panel.grid.major.y = ggplot2::element_line(color="#cbcbcb"),
    panel.grid.major.x = ggplot2::element_blank(),
    
    #Blank background
    #This sets the panel background as blank, removing the standard grey ggplot background colour from the plot
    panel.background = ggplot2::element_blank(),
    #Strip background (#This sets the panel background for facet-wrapped plots to white, removing the standard grey ggplot background colour and sets the title size of the facet-wrap title to font size 22)
    strip.background = ggplot2::element_rect(fill="white"),
    strip.text = ggplot2::element_text(size  = 22,  hjust = 0)
  )
}

```



### 1.3 data

* source : https://blog.twitter.com/en_us/topics/company/2019/information_operations_directed_at_Hong_Kong.html。
    * 推特官方已刪除資料集，原始檔[連結](https://drive.google.com/drive/folders/1YcF1GjzbtlcAydJWx5HU68X0ueWsK8gL?usp=sharing)
    * 資料集分成set1、set2，每個set裡面分別有帳號集以及推文集(tweets)
    * assign成四個dataframe(set1,set2,set1_content,set2_content)
    * 若電腦不夠存，`load(file = "twitterdata.rda")`


```{r echo=TRUE}
##dataset of delected accounts
#set1 <- read.csv("data/china_082019_1_users_csv_hashed.csv")
#set2 <- read.csv("data/china_082019_2_users_csv_hashed.csv")
##tweets content from delected accounts
#set1_content <- read.csv("data/china_082019_1_tweets_csv_hashed.csv")
#set2_content <- read.csv("data/china_082019_2_tweets_csv_hashed.csv")
load(file = "twitterdata.rda")
```


## 02 An overview of whole dataset

### 2.1 stucture 

```{r echo=TRUE, results = "hide"}
#observation
str(set1)
colnames(set1_content)
head(set2_content)
```

```{r echo=TRUE}

#ask a question:cration_date for example, compare with follower_count
set1$account_creation_date %>% summary()
class(set1$account_creation_date)
set1$follower_count %>% summary()

```

### 2.2 preprocessing 

#### `Time`

package `lubridate`

| order of elements in date-time | parse function | 
|-------|------|
| year month day | ymd() |
| year day month |ydm() | 
| month day year |mdy() |
| day month year | dmy() | 
| hour minute | hm() | 
| hour minute second | hms() | 
| year month day hour minute second | ymd_hms() | 


```{r echo=TRUE}
head(set1_content$account_creation_date)
#base::chr to POSIXct
set1$account_creation_date <- as.POSIXct(strptime(set1$account_creation_date,"%Y-%m-%d"))
set2$account_creation_date <- as.POSIXct(strptime(set2$account_creation_date,"%Y-%m-%d"))
#lubridate::
set1 %>%
  mutate(creation_date = ymd(account_creation_date))%>%
  select(creation_date)%>%summary()
set1 <- set1%>%
  mutate(account_creation_date = ymd(account_creation_date))
#check if successfully convert to POSIXct
class(set1$account_creation_date)
```

| account_creation_date | creation_date| 
|-------|------|
| Min.   :2008-05-16<br>1st Qu.:2016-06-27  <br>Median :2017-08-30<br> Mean   :2016-08-22<br>3rd Qu.:2017-10-17 <br>Max.   :2019-05-07 | Length<br>Class Mode <br>744 character<br>character  |

### 2.3 time series of account_creation_date

```{r}
options(scipen = 999)
#plot version1
set1 %>%
  ggplot() + 
  aes(account_creation_date) + 
  geom_density(color = brewer.pal(7, "Set3")[4])+
  labs(x = "account creation date" , y = "N",title = "Set1帳號成立時間")+
  theme(text = element_text(family = "Gen Jyuu GothicX")) +bbc_style_cn()
#plot version2
set1 %>%
    ggplot(aes(account_creation_date)) +
    geom_histogram(bins=80,fill="lightblue") +
    labs(title = "The Date Accounts Created",subtitle = "dataset:set1")+
    bbc_style()+
    geom_vline(xintercept = as.Date(c("2019-02-01")), color="red", alpha=0.5)
#set2 account
set2 %>%
  ggplot() + 
  aes(account_creation_date) + 
  geom_density(color = brewer.pal(7, "Set3")[4])+
  labs(x = "時間" , y = "數量",title = "Set2帳號成立時間")+
  theme(text = element_text(family = "Gen Jyuu GothicX"))+bbc_style_cn()
#count the peak
set1 %>%
  count(account_creation_date) %>%
  arrange(-n)%>%
  mutate(portion = n/sum(n))
#filter the arrange
set1 %>%
  filter(account_creation_date == "2017-08-30")%>%
  arrange(-follower_count)%>%
  select(userid,follower_count,following_count)
```

### 2.4 account language
```{r}
set1 %>%
  count(account_language) %>%
  arrange(-n)%>%
  mutate(portion = n/sum(n))
#plot
set1 %>%
  count(account_language) %>%
  mutate(portion = n/sum(n))%>%
  ggplot(aes(x = reorder(account_language, n), y = n, fill = ifelse(account_language == "zh-cn", "h","l")))+
  geom_bar(stat = "identity")+
  labs(title = "The Languages",subtitle = "dataset: set1")+ scale_fill_manual( values = c( "h"="orange", "l"="lightblue" ), guide = FALSE)+
  geom_hline(yintercept = 0, size = 1, colour="grey") +
  coord_flip() +
  bbc_style()

```


### 2.5 follow difference
#### 2.5.1 plot
* using following as x, follower as y

```{r}
#add dataset lable
set1_follow <- set1 %>%
  select(userid,follower_count,following_count)%>%
  mutate(dataset = factor(rep("set1",length(nrow(set1)))))
set2_follow <- set2 %>%
  select(userid,follower_count,following_count)%>%
  mutate(dataset = factor(rep("set2",length(nrow(set2)))))
#bind two dataset
all_follow <- set2_follow %>%
  bind_rows(set1_follow)
all_follow <- all_follow  %>%
  mutate(dataset = factor(rep("delected account",length(nrow(all_follow)))))
#plot set1&set2 
options(scipen = 999)
ggplot(all_follow,aes(x = following_count,y = follower_count))+
  geom_point(position = "jitter",size=2.5, colour = "#E69F00",alpha = 0.8)+ 
  labs(title = "The distribution of follow",subtitle = "dataset: set1&set2")+
  xlim(0,15000)+ylim(0,20000)+ scale_color_manual(values="#E69F00")+bbc_style()

```
#### 2.5.2 compare to normal

normal account of twitter:
https://twitter.com/conspirator0/status/1149851150658748416
```{r error=FALSE, message=FALSE,results = "hide"}

#plot
load("twitter_random.rds")
random_user.df <- random_user.df %>%
  mutate(dataset = factor(rep("random account",length(nrow(random_user.df)))))%>%
  rename(userid = random_name.i...)
random_user.df%>%  
  bind_rows(all_follow)%>%
  ggplot(aes(x = following_count,y = follower_count,color=dataset))+
  geom_point(position = "jitter",size=2,alpha = 0.7)+ 
  scale_colour_manual(values=c("blue", "cyan4")) + 
  labs(title = "The distribution of follow",subtitle = "dataset: set1&set2")+
  xlim(0,15000)+ylim(0,20000)+ scale_color_manual(values=c("#E69F00", "#56B4E9"))+bbc_style()
```


## 03 An overview of 反送中account

### 3.1 filter account

```{r}
#join set1_content & set2_content
all_tweet <- bind_rows(set1_content%>%mutate(dataset = factor(rep("set1",length(nrow(set1_content))))),set2_content%>%mutate(dataset = factor(rep("set2",length(nrow(set2_content))))))%>%
  select(-poll_choices)
#filter relevant
hk_relevant_tweet <- all_tweet%>%
  mutate(tweet_time = as.POSIXct(strptime(tweet_time, "%Y-%m-%d %M:%S")))%>%
  filter(tweet_time > as.Date("2019-01-01"))%>%
  filter(str_detect(tweet_text, "香港警察|港警|逃犯條例|反修例|遊行|修例|反送中|anti-extradition"))
#how many accounts relevant to anti-extradition
hk_relevant_tweet%>%
  group_by(dataset)%>%
  count()
#filter set2
hk_relevant_tweet%>%
  filter(dataset == "set2")
```

```{r}
#practice filter anti-extradition
set2_content %>%
  filter(tweet_time > as.Date("2019-01-01")) %>%
  filter(str_detect(tweet_text, "反送中|anti-extradition"))
```

### 3.2 frequency word
example:tweets contains "反送中|anti-extradition"
```{r}
segment_not <- c("反送中", "送中條例", "香港人", "支持警察", "革命派", "勇武派", "人權", "泛民", "严惩", "暴乱", "力撑", "港警", "撐警集會", "法治社会", "逃犯条例", "逃犯條例", "警队加油", "警队", "香港加油","反對派","反对派","林鄭","林鄭月娥","做對","做对","夏悫道","龙道","撐政府","香港警察")
cutter <- worker()
new_user_word(cutter, segment_not)
stopWords <- read.csv("data/stopwords_hk.csv")
names(stopWords) <- "word"
# 斷詞
tokens <-  hk_relevant_tweet%>%
  select(tweetid,tweet_time,tweet_text)%>%
  mutate(word = purrr::map(tweet_text, function(x)segment(x, cutter)))%>%
  unnest(word)%>%
  filter(!(word %in% stopWords$word)) %>%
  filter(!str_detect(word, "[a-zA-Z0-9]+"))
# count
tokens %>%
  select(word)%>%
  count(word, sort = TRUE) %>%
  head(20)%>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col(fill = "royalblue") +
  labs(title = "反送中相關推文詞頻",subtitle = "dataset:set1&set2") +
  theme(axis.text.y = ggplot2::element_text(hjust = 0.9,size = 10)) +
  coord_flip() + 
  bbc_style_cn()

```


